\chapter{Exercise 02}
\extitle{The logger}
\turnindir{ex02}
\exnumber{02}
\exfiles{logger.py}
\exforbidden{None}
\makeheaderfilesforbidden

% ================================= %
\section*{Objective}
% --------------------------------- %
In this exercise, you will learn about decorators and we are not talking about 
the decoration of your room.\\
\\
The \texttt{@log} will write info about the decorated function in a
\texttt{machine.log} file.\\
\\
% ================================= %
\section*{Instructions}
% --------------------------------- %
You have to create the log decorator in the same file.\\
\\
Pay attention to all the different actions logged at the call of
each method. You may notice the username from environment
variables is written to the log file.\\
\\

\begin{minted}[bgcolor=darcula-back,formatcom=\color{lightgrey},fontsize=\scriptsize]{python}
import time
from random import randint
import os

#... your definition of log decorator...

class CoffeeMachine():

	water_level = 100

	@log
	def start_machine(self):
	  if self.water_level > 20:
		  return True
	  else:
		  print("Please add water!")
		  return False
	
	@log
	def boil_water(self):
		return "boiling..."
	
	@log
	def make_coffee(self):
		if self.start_machine():
			for _ in range(20):
				time.sleep(0.1)
				self.water_level -= 1
			print(self.boil_water())
			print("Coffee is ready!")
	
	@log
	def add_water(self, water_level):
		time.sleep(randint(1, 5))
		self.water_level += water_level
		print("Blub blub blub...")


if __name__ == "__main__":
	
	machine = CoffeeMachine()
	for i in range(0, 5):
		machine.make_coffee()

	machine.make_coffee()
	machine.add_water(70)
\end{minted}

% ================================= %
\section*{Examples}
% --------------------------------- %
\begin{42console}
  $> python logger.py
  boiling...
  Coffee is ready!
  boiling...
  Coffee is ready!
  boiling...
  Coffee is ready!
  boiling...
  Coffee is ready!
  Please add water!
  Please add water!
  Blub blub blub...
  $>
\end{42console}

\begin{42console}
  $> cat machine.log
  (cmaxime)Running: Start Machine      [ exec-time = 0.001 ms ]
  (cmaxime)Running: Boil Water         [ exec-time = 0.005 ms ]
  (cmaxime)Running: Make Coffee        [ exec-time = 2.499 s  ]
  (cmaxime)Running: Start Machine      [ exec-time = 0.002 ms ]
  (cmaxime)Running: Boil Water         [ exec-time = 0.005 ms ]
  (cmaxime)Running: Make Coffee        [ exec-time = 2.618 s  ]
  (cmaxime)Running: Start Machine      [ exec-time = 0.003 ms ]
  (cmaxime)Running: Boil Water         [ exec-time = 0.004 ms ]
  (cmaxime)Running: Make Coffee        [ exec-time = 2.676 s  ]
  (cmaxime)Running: Start Machine      [ exec-time = 0.003 ms ]
  (cmaxime)Running: Boil Water         [ exec-time = 0.004 ms ]
  (cmaxime)Running: Make Coffee        [ exec-time = 2.648 s  ]
  (cmaxime)Running: Start Machine      [ exec-time = 0.011 ms ]
  (cmaxime)Running: Make Coffee        [ exec-time = 0.029 ms ]
  (cmaxime)Running: Start Machine      [ exec-time = 0.009 ms ]
  (cmaxime)Running: Make Coffee        [ exec-time = 0.024 ms ]
  (cmaxime)Running: Add Water          [ exec-time = 5.026 s  ]
  $>
\end{42console}
Pay attention, the length between ":" and "[" is 20].
Draw the corresponding conclusions on this part of a log entry.
