\chapter{Exercise 05}
\extitle{TinyStatistician}
\turnindir{ex05}
\exnumber{05}
\exfiles{TinyStatistician.py}
\exforbidden{Any function that calculates mean, median, quartiles, variance or standar deviation for you.}
\makeheaderfilesforbidden


% ================================= %
\section*{Objective}
% --------------------------------- %
Initiation to very basic statistic notions.

% ================================= %
\section*{Instructions}
% --------------------------------- %
Create a class named \texttt{TinyStatistician} that implements the following methods:
\begin{itemize}
  \item \texttt{mean(x)}: computes the mean of a given non-empty list or array \texttt{x}, using a for-loop.
  The method returns the mean as a float, otherwise \texttt{None} if \texttt{x} is an empty list or array.
  Given a vector \texttt{x} of dimension $m \times 1$, the mathematical formula of its mean is:
  $$
  \mu = \frac{\sum_{i = 1}^{m}{x_i}}{m}
  $$
  \item \texttt{median(x)}: computes the median of a given non-empty list or array \texttt{x}.
  The method returns the median as a float, otherwise \texttt{None} if \texttt{x} is an empty list or array. 
  \item \texttt{quartiles(x)}: computes the $1^{\text{st}}$ and $3^{\text{rd}}$ quartiles of a given non-empty array \texttt{x}.
  The method returns the quartile as a float, otherwise \texttt{None} if \texttt{x} is an empty list or array.
  \item \texttt{var(x)}: computes the variance of a given non-empty list or array \texttt{x}, using a for-loop.
  The method returns the variance as a float, otherwise \texttt{None} if \texttt{x} is an empty list or array.
  Given a vector \texttt{x} of dimension $m \times 1$, the mathematical formula of its variance is:
  $$
  \sigma^2 = \frac{\sum_{i = 1}^{m}{(x_i - \mu)^2}}{m} = \frac{\sum_{i = 1}^{m}{[x_i - (\frac{1}{m}\sum_{j = 1}^{m}{x_j}})]^2}{m}
  $$
  \item \texttt{std(x)} : computes the standard deviation of a given non-empty list or array \texttt{x}, using a for-loop.
  The method returns the standard deviation as a float, otherwise \texttt{None} if \texttt{x} is an empty list or array.
  Given a vector \texttt{x} of dimension $m \times 1$, the mathematical formula of its standard deviation is:
  $$
  \sigma = \sqrt{\frac{\sum_{i = 1}^{m}{(x_i - \mu)^2}}{m}} = \sqrt{\frac{\sum_{i = 1}^{m}{[x_i - (\frac{1}{m}\sum_{j = 1}^{m}{x_j}})]^2}{m}}
  $$
\end{itemize}
All methods take a \texttt{list} or a \texttt{numpy.ndarray} as parameter.\\
\\
We are assuming that all inputs have a correct format, i.e. a list or array of numeric type or empty list or array.\\
\\
You don't have to protect your functions against input errors.
\\
% ================================= %
\section*{Examples}
% --------------------------------- %
\begin{minted}[bgcolor=darcula-back,formatcom=\color{lightgrey},fontsize=\scriptsize]{python}
from TinyStatistician import TinyStatistician
tstat = TinyStatistician()
a = [1, 42, 300, 10, 59]

tstat.mean(a)
# Expected result: 82.4

tstat.median(a)
# Expected result: 42.0

tstat.quartile(a)
# Expected result: [10.0, 59.0]

tstat.var(a)
# Expected result: 12279.439999999999

tstat.std(a)
# Expected result: 110.81263465868862  
\end{minted}