%******************************************************************************%
%                                                                              %
%                        Common Instructions                                   %
%                    for Piscine rushes Projects                               %
%                                                                              %
%******************************************************************************%

\item \underline{The group WILL be registered to defense automatically.}

\item \underline{Do not cancel it, you won't get a second one.}

\item Any question concerning the subject would complicate the subject.

\item You have to follow the \underline{submission procedures} for all your
    exercises.

\item This subject could change up to an hour before submission.

\item If there is a moulinette, it will compiles with the following flags: -Wall -Wextra -Werror; and uses \texttt{cc}.

\item If your program doesn’t compile, you’ll get \texttt{0}.

\item You must therefore do the project with the imposed team and show up
    at Your defense slot, with \underline{all} of your teammates.

\item You project must be done by the time you get to defense. The purpose
    of defense is for you to present and explain your work.

\item Each member of your group must be fully aware of the works of the project.
    Should you choose to split the workload, make sure you all understand what
    everybody's done. During the defense, you'll be asked questions and the final
    grade will be based on the worst explanations.

\item It goes without saying, but gathering the group is your responsibility.
    You've got all the means to get in contact with your teammates: phone, email, carrier pigeon,
    spiritism, etc. So don't bother blurping up excuses. Life isn't fair,
    that's just the way it is.

\item However, if you've \underline{really tried everything} one of your teammates
    remains unreachable: do the project anyway, and we'll try and see what we can do
    about it during the defense. Even if the group leader is missing, you still have
    access to the submission directory.

\item Your work must respect the Norm. Be thourough.